Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-12 talk/pepm2011/paper.tex
related work

\newcommand\ie{i.e.,\xspace}
\newcommand\eg{e.g.,\xspace}

@@

Escape analysis: XXX

@@

hint in first js paper by michael franz \cite{mason_chang_efficient_2007}

>>>>

\newcommand\ie{i.e.,\xspace}
\newcommand\eg{e.g.,\xspace}
\newcommand{\etal}{\emph{et al.}\xspace}

@@

There exists a large number of works on escape analysis, which is an program
analysis that tries to find an upper bound for the lifetime of objects allocated
at specific program points
\cite{goldberg_higher_1990,park_escape_1992,choi_escape_1999,bruno_blanchet_escape_2003}.
This information can then be used to decide that certain objects can be
allocated on the stack, because their lifetime does not exceed that of the stack
frame it is allocated in. The difference to our work is that escape analysis is
split into an analysis and an optimization phase. The analysis can be a lot more
complex than our simple one-pass optimization. Also, stack-allocation reduces
garbage-collection pressure but does not optimize away the actual accesses to
the stack-allocated object. In our case, an object is not needed at all any
more.
XXX more papers?

Chang \etal describe a tracing JIT for JavaScript running on top of a JVM
\cite{mason_chang_efficient_2007}. They mention in passing an approach to
allocation removal that moves the allocation of an object of type 1 out of the
loop to only allocate it once, instead of every iteration. No details are given
for this optimization. The fact that the object is still allocated and needs to
be written to means that only the allocations are optimized away, but not the
reads and writes out of/into the object.

@@
